Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-08 edubots_surveys.Rnw
Fix by @noorhanabbas closes #64 also #50
Add highlight
minor fixes refs#48

%Why messaging apps are relevant here --> connect to the development of chatbots
Group messaging apps have become a powerful tool for keeping touch with
students. Also, many of them have built-in chatbots to enhance the learning
process. After an initial analysis to the answers to the first survey, we
realized that there were some prior issues mainly related to the adoption of a
technology, chatbots, that generally piggybacks on another, messaging
applications. In a technology adoption model, perceived ease of use and
perceived usefulness are essential. But it is going to be very difficult for
teachers to find {\em chatbots} easy to use if they, previously, do not
consider, or simply use, the messaging tools to which they are attached.

@@

Finally, a two-step cluster analysis was conducted, with a log-likelihood
distance measure adopted, to explore how the cases could be grouped based on
their preferences of specific interaction media features, and which features
have larger predictor importance for the clustering (see
Fig. \ref{figure:predictor}). Two clusters occurred from the analysis: cluster 1
(n=78, 60.9\%) was comprise of instructors who did not value interaction media
pluggability, connectivity, official formation, but valued interaction media
analytics, familiarity, support by the institution, while cluster 2 (n=50,
39.1\%) was comprise of instructors from which the majority did not value media
analytics, official formation, familiarity, but valued pluggability,
connectivity, and support by the institution. Interaction media pluggability
appears to have the most important predictor importance in the clustering of
cases (predictor importance = 1.0), whilst media unidirectionality was the least
important factor (predictor importance = 0.04). The cluster quality is fair, but
not a good one (silhouette measure of cohesion and separation).

@@

 One of the most interesting questions that can arise from the analysis of the
 results, and that should require further study, is: Are teachers really aware
 of the possibilities of chatbots in the classroom? The reason to ask ourselves
 this question is due to the fact of the small number of responses for other
 uses in comparison with the other approaches proposed. Another way to look
 about it is that, unless you provide the specific instructions on how to use a
 tool, the teaching staff is already too busy or burn out to think about
 innovation.

It is also likely that their opinions towards chatbots are informed by negative
experiences with customer support chatbots, which is what most people will have
experienced. This will probably require further study, but also will need to be
taken into account when introducing chatbot technologies in the classroom: it
will have to be as simple, and as satisfactory, ad possible, to (possibly)
delete this existing perception.

>>>>

Group messaging apps have become a powerful tool for \textcolor{blue}{communicating} with
students. Also, many of them have built-in chatbots to enhance the learning
process. After an initial analysis to the answers to the first survey, we
realized that there were some prior issues mainly related to the adoption of a
technology, chatbots, that generally piggybacks on another, messaging
applications. In a technology adoption model, perceived ease of use and
perceived usefulness are essential. But it is going to be very difficult for
teachers to find {\em chatbots} easy to use if they, previously, do not
consider, or simply use, the messaging tools to which they are attached.

@@

Finally, a two-step cluster analysis was conducted, with a log-likelihood
distance measure adopted, to explore how the cases could be grouped based on
their preferences of specific interaction media features, and which features
have larger predictor importance for the clustering (see
Fig. \ref{figure:predictor}). Two clusters occurred from the analysis: cluster 1
(n=78, 60.9\%) is formed with instructors who did not value interaction media
pluggability, connectivity, official formation, but valued interaction media
analytics, familiarity, support by the institution; cluster 2 (n=50,
39.1\%) groups instructors that did not value media
analytics, official formation, familiarity, but valued pluggability,
connectivity, and support by the institution. Interaction media pluggability
appears to have the most important predictor importance in the clustering of
cases (predictor importance = 1.0), whilst media unidirectionality was the least
important factor (predictor importance = 0.04). The cluster quality is fair, but
not a good one (silhouette measure of cohesion and separation).

@@

One of the most interesting questions that can arise from the analysis of the
results, and that should require further study, is: Are teachers really aware
of the possibilities of chatbots in the classroom? \textcolor{blue}{The survey 
only listed a few functionalities for the chatbots and only a few subjects selected 
the option "Others". This may suggest  that most teachers did not really understand 
at this point the actual potential of chatbots.} Another way to look about it is 
that, unless you provide the specific instructions on how to use a
tool, the teaching staff is already too busy or burn out to think about
innovation.

It is also likely that their opinions towards chatbots are informed by negative
experiences with customer support chatbots, which is what most people will have
experienced. This will probably require further study, but also will need to be
taken into account when introducing chatbot technologies in the classroom: 
\textcolor{blue}{it will have to be as simple, and as satisfactory, as possible, 
to (possibly) change this existing perception}.
